### 2020-12-20 paper/model/initial_conditions.tex
minor ameliorations.

Consider a situation where you want to start a simulation with the beginning set amidst the pandemic. It means that several thousands of individuals have already recovered from the disease, are infectious, symptomatic or in ICUs. Additionally, the sample of infectious people who will determine the course of the pandemic in the following periods is likely not representative of the whole population because of differences in behavior (number of contacts, assortativeness), past policies (school closures), etc.. The distribution of courses of diseases in the population at the begin of the simulation are called initial conditions.

To come up with realistic initial conditions, we match reported infections from official data to simulated individuals by available characteristics like age and geographic information. The matching must be done for each day of a longer time frame like a month to have individuals in all possible health states. Then, health statuses evolve until the begin of the simulation period without simulating infections by contacts. It is also possible to correct reported infections for a reporting lag and scale them up to arrive at the true number of infections.

>>>>

Consider a situation where you want to start a simulation with the beginning set amidst the pandemic. It means that several thousands of individuals have already recovered from the disease, are infectious, symptomatic or in ICUs. Additionally, the sample of infectious people who will determine the course of the pandemic in the following periods is likely not representative of the whole population because of differences in behavior (number of contacts, assortativeness), past policies (school closures), etc.. The distribution of courses of diseases in the population at the begin of the simulation is called initial conditions.

To come up with realistic initial conditions, we match reported infections from official data to simulated individuals by available characteristics like age and geographic information. The matching must be done for each day of a longer time frame like a month to have individuals with possible health states. Then, health statuses evolve until the begin of the simulation period without simulating infections by contacts. It is also possible to correct reported infections for a reporting lag and scale them up to arrive at the true number of infections.

### 2020-12-20 paper/model/summary.tex
minor ameliorations.

There are two possible ways to enable testing for Covid-19 in the model. The first way allows to specify the ratio of known to unknown infections for each day. A random sample of all newly infected individuals will then receive a test result in the following days. The second approach allows people who experience symptoms or people who had a risk contact can demand a test. Test allocation models assign tests to individuals while also respecting the capacities. Test processing models determine in which order the tests are processed and when infected individuals are notified.

@@

>>>>

There are two possible ways to enable testing for Covid-19 in the model. The first way allows to specify the ratio of known to unknown infections for each day. A random sample of all newly infected individuals will then receive a test result in the following days. The second approach consists of three steps. First, individuals demand a test because they, e.g., experience symptoms. Secondly, tests are allocated to individuals while respecting governmental access restrictions to test. Thirdly, depending of the capacities of laboratories, tests are processed for some time until the individual receives her test result.

@@

Last but not least, performing simulations whose starting point is set amidst the pandemic requires special adjustments to arrive at a realistic distribution of courses of diseases. We solve the initial conditions problem by matching reported infections to individuals in our data while also correcting for reporting lag and undetected cases.
